### 2022-10-01 Papers/ICCC-2023/sections/design.tex
more stuff

@@

C-=-1 type system heavily borrows from C++.

@@

>>>>

C-=-1 is a simple language, built with the minimum set of features needed to demonstrate the usefulness of the proposed metaprogramming features.

@@

C-=-1 type system heavily borrows from C++.
Program may contain user defined classes, with members which may have limited accessibility.
Generic programming is achieved by the use of templates, although they are mutch more limited than the ones present in C++.
The user may also use pointers to objects, with arbitrary indirection (for example pointer to pointer to object).
Additionally, the language contains the concept of an \lstinline{interface}, similar to the one found in C\#.

@@

To declare an attribute in C-=-1, the \lstinline{att} keyword is used.
After that, attribute targets should be listed in angled brackets, as on line 0 of Listing \ref{lst:noDiscardCm1}.
Attributes may target any number of language elements, including types, functions, variables and fields.
Attribute from Listing \ref{lst:noDiscardCm1} declares two member functions: \lstinline{attach} on line 4 and \lstinline{onCall} on line 6.

The \lstinline{attach} method is called after names of all of the program elements have been gathered, but before the compiler started to analyze function bodies.
It is common accross all attribute targets and accepts the descriptor of the attached program element (function, field, type, etc.).
Only during call to \lstinline{attach} can the attribute change aspects of the program that affect function overload resolution, for example
whether a function is invokable at run or compile time.

The \lstinline{onCall} method is an example of a function reacting to usage of the annotated program element.
They are speciffic to a given attribute target.
Within this function, the attribute may analyze and modify the code, as well as raise errors or warnings.
